Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
removed space in citation
more revision

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability %, working typically on continuous domains
\cite{sadabadi2016static, DBLP:journals/corr/AbateBCCDKK16}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.

Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.
In this paper, however, we propose the synthesis of control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant, alongside the discrete domain of the controller and the
hybrid elements that communicate them.

In this paper, we synthesize controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{safe}.  Due to the complexity of such systems, in this work we focus
on linear models with known configurations and perform parametric synthesis
of safe digital controllers.
To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of abstraction refinement
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

\textcolor{red}{Cristina: Can you please further expand the introduction
by adding more details about our synthesis approach to control systems?}

@@

\todo{[Move material from \ref{sec:rw} here]}

@@

%-------------------------------
\section{Related Work}
\label{sec:rw}
%-------------------------------

\textcolor{red}{LC: Cristina and Dario, should we further expand this section with other initiatives to synthesise control systems?}

>>>>

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability %, working typically on continuous domains
\cite{sadabadi2016static,DBLP:journals/corr/AbateBCCDKK16}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.

In this paper, we propose the synthesis of \emph{safe} control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant, alongside the discrete domain of the controller and the
hybrid elements that communicate them.
%
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus
on linear models with known configurations and perform parametric synthesis
of safe digital controllers.

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of abstraction refinement
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

%% \textcolor{red}{Cristina: Can you please further expand the introduction
%% by adding more details about our synthesis approach to control systems?}

@@

%\todo{[Move material from \ref{sec:rw} here]}

@@

%% %-------------------------------
%% \section{Related Work}
%% \label{sec:rw}
%% %-------------------------------
